Interfering with Noninterference \iftext\thanks{\bcp{Identify applicable funding agencies here (DARPA and NSF and...?)}}\fi

### 2020-01-07 main.tex
Strong noninterference ref from chalmers/PLAS

\iftext
\author{\IEEEauthorblockN{Roberto Blanco}
\IEEEauthorblockA{\textit{\bcp{affiliation?}}
% \textit{name of organization (of Aff.)}\\
% City, Country \\
% email address or ORCID
}
\and
\IEEEauthorblockN{Leonidas Lampropoulos}
\IEEEauthorblockA{\textit{University of Maryland \bcp{right?}}
% \textit{name of organization (of Aff.)}\\
% City, Country \\
% email address or ORCID
  }
\and
\IEEEauthorblockN{Benjamin C. Pierce}
\IEEEauthorblockA{\textit{University of Pennsylvania}
% \textit{name of organization (of Aff.)}\\
% City, Country \\
% email address or ORCID
  }
\and
\IEEEauthorblockN{Andrew Tolmach}
\IEEEauthorblockA{\textit{Portland State University}
% \textit{name of organization (of Aff.)}\\
% City, Country \\
% email address or ORCID
}
}
\fi

@@

A {\em topography}\bcp{??}
$\topo \in (\WORDS \cup \REGS \cup \{\PCname\}) \rightarrow \{\HIGH,\LOW\}$ is a
map from machine components to ``security levels,'' where $\HIGH$ marks
locations containing secret or low-integrity data and $\LOW$ marks those
with public or high-integrity data.

@@

>>>>

\iftext
\IEEEauthorblockN{Leonidas Lampropoulos}
\IEEEauthorblockA{\textit{University of Maryland \bcp{right?}}
% \textit{name of organization (of Aff.)}\\
% City, Country \\
% email address or ORCID
  }
\and
\author{\IEEEauthorblockN{Roberto Blanco}
\IEEEauthorblockA{\textit{\bcp{affiliation?}}
% \textit{name of organization (of Aff.)}\\
% City, Country \\
% email address or ORCID
}
\and
\IEEEauthorblockN{Benjamin C. Pierce}
\IEEEauthorblockA{\textit{University of Pennsylvania}
% \textit{name of organization (of Aff.)}\\
% City, Country \\
% email address or ORCID
  }
\and
\IEEEauthorblockN{Andrew Tolmach}
\IEEEauthorblockA{\textit{Portland State University}
% \textit{name of organization (of Aff.)}\\
% City, Country \\
% email address or ORCID
}
}
\fi

@@

A {\em topography}\bcp{contour!}
$\topo \in (\WORDS \cup \REGS \cup \{\PCname\}) \rightarrow \{\HIGH,\LOW\}$ is a
map from machine components to ``security levels,'' where $\HIGH$ marks
locations containing secret or low-integrity data and $\LOW$ marks those
with public or high-integrity data.

@@

\item Simple Noninterference by Normalization {http://nachivpn.me/nibnbe.pdf}
